---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
pkgload::load_all(quiet = TRUE, helpers = FALSE, export_all = FALSE, 
                  warn_conflicts = FALSE, reset = TRUE)
```

# socialGH

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/llrs/socialGH/branch/master/graph/badge.svg)](https://codecov.io/gh/llrs/socialGH?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of socialGH is to help extracting information from social relations on repositories on GitHub.

## Installation

You can install the released version of socialGH from GitHub with:

``` r
remotes::install_github("llrs/socialGH")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE, include=TRUE}
library(socialGH)
```

You can download issues (does not include comments made on them), pull requests (PR), events, and comments on issues and PR.

```{r issues}
get_issues("llrs/socialGH")
```
